Manuscript

### 2015-03-10 inst/simulation/manuscript.Rmd
...

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- (1 - nrow(cutoffPopulationSizes(x, overEstimate)) / nrow(x)) * 100
      #(sum(x$Estimated < overEstimate[1] | x$Estimated > overEstimate[2]) / nrow(x)) * 100)
    x <- cutoffPopulationSizes(x, overEstimate)
    #subset(x, Estimated <= overEstimate)
    #if (x$modelName[1] == "FMPModel") failed <- NA
    #if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, SlopeSD=NA, R2=NA, Failed=failed, EstTrue=NA, EstTrueSD=NA, EstTrueMin=NA, EstTrueMax=NA, N=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(log(x$Estimated/x$Observed))
    prop.sd <- sd(log(x$Estimated/x$Observed))
    prop.min <- quantile(log(x$Estimated/x$Observed), .05)
    prop.max <- quantile(log(x$Estimated/x$Observed), .95)
    slope.sd <- coef(summary(y))[2,2]
    return(data.frame(Intercept=coef(y)[1], Slope=coef(y)[2], SlopeSD=slope.sd, R2=summary(y)$r.squared, EstTrue=prop.mean, EstTrueSD=prop.sd, EstTrueMin=prop.min, EstTrueMax=prop.max, Failed=failed, N=nrow(x)))
  }, overEstimate=overEstimate)

@@

rer.stat <- function(x) data.frame(SizeCount=mean(x$intersections/x$Observed),
                                   SizeCountMin=quantile(x$intersections/x$Observed, 0.05),
                                   SizeCountMax=quantile(x$intersections/x$Observed, 0.95))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario); i$Case <- "1"
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario); i2000$Case <- "2"
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario); i10days$Case <- "3"

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray", "gray"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal")
  return(p)
}
```

>>>>

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- (1 - nrow(cutoffPopulationSizes(x, overEstimate)) / nrow(x)) * 100
      #(sum(x$Estimated < overEstimate[1] | x$Estimated > overEstimate[2]) / nrow(x)) * 100)
    x <- cutoffPopulationSizes(x, overEstimate)
    #subset(x, Estimated <= overEstimate)
    #if (x$modelName[1] == "FMPModel") failed <- NA
    #if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, SlopeSD=NA, R2=NA, Failed=failed, EstTrue=NA, EstTrueSD=NA, EstTrueMin=NA, EstTrueMax=NA, N=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(log(x$Estimated/x$Observed))
    prop.sd <- sd(log(x$Estimated/x$Observed))
    prop.min <- quantile(log(x$Estimated/x$Observed), .025)
    prop.max <- quantile(log(x$Estimated/x$Observed), .975)
    slope.sd <- coef(summary(y))[2,2]
    return(data.frame(Intercept=coef(y)[1], Slope=coef(y)[2], SlopeSD=slope.sd, R2=summary(y)$r.squared, EstTrue=prop.mean, EstTrueSD=prop.sd, EstTrueMin=prop.min, EstTrueMax=prop.max, Failed=failed, N=nrow(x)))
  }, overEstimate=overEstimate)

@@

rer.stat <- function(x) data.frame(SizeCount=mean(x$intersections/x$Observed),
                                   SizeCountMin=quantile(x$intersections/x$Observed, 0.025),
                                   SizeCountMax=quantile(x$intersections/x$Observed, 0.975))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario); i$Case <- "1"
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario); i2000$Case <- "2"
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario); i10days$Case <- "3"

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) +
    #scale_colour_manual("Model", values=c("black", "darkgray", "gray"), labels=modelLabels) +
    scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal")
  return(p)
}
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2, dpi=200)
```
